The MolSSI \qca Project: An open-source platform to compute, organize, and share quantum chemistry data

### 2020-05-16 response2.tex
From DGAS: I swapped out Figure 10 with a more up to date version. The changes are largely cosmetic, but does switch functionals to represent a more complete visualization. I left the original version there as well if its not possible to change the figure.
Noted DGAS's update of Fig. 10. -TDC

\noindent \underline{Author Response:} \textit{We have had several
conversations with PubChem and Citrine about cross referencing data, but this
has not yet been complete, and thus we feel it would be premature to comment
on this in the manuscript.  \qcfN interacts exclusively over standard
TCP/IP (HTTP/REST) protocols that can be accessed from any language as
discussed briefly in Fig 4.}

@@

\noindent
\textcolor{red}{(63) Becke, A. D. Density-functional thermochemistry. III. The
role of exact exchange. J. Chem. Phys. 1993, 98, 5648–5652.}

\noindent
\textcolor{red}{(64) Lee, C.; Yang, W.; Parr, R. G. Development of the Colle-Salvetti
correlation-energy formula into a functional of the electron density. Phys. Rev.
B. 1988, 37, 785–789.}

@@

>>>>

\noindent \underline{Author Response:} \textit{We have had several
conversations with PubChem and Citrine about cross referencing data, but this
has not yet been complete, and thus we feel it would be premature to comment
on this in the manuscript.  \qcfN~interacts exclusively over standard
TCP/IP (HTTP/REST) protocols that can be accessed from any language as
discussed briefly in Fig 4.}

@@

\noindent
\textcolor{red}{(66) Becke, A. D. Density-functional thermochemistry. III. The
role of exact exchange. J. Chem. Phys. 1993, 98, 5648–5652.}

\noindent
\textcolor{red}{(67) Lee, C.; Yang, W.; Parr, R. G. Development of the Colle-Salvetti
correlation-energy formula into a functional of the electron density. Phys. Rev.
B. 1988, 37, 785–789.}

@@

\noindent
\textbf{Other Changes:}

\noindent \textit{We have updated Figure 10 to provide a more complete visualization of the application.}
